---
title: "Week 1 Blog"
author: "Angelina Evans"
date: "2023-05-23"
categories: "Week One"
---

# My first week with DSPG

During week one, I took a couple data camp courses to get more familiar with topics in R, Github, and web scraping in R.

Here is an example of what I did in the Intro to R course. In the code below, there are two vectors: scores and comments.

```{r}
scores <- c(4.6, 5, 4.8, 5, 4.2)
comments <- c("I would watch it again", "Amazing!", "I liked it", "One of the best movies", "Fascinating plot")

```

I can get the mean of the scores vector by writing:

```{r}
mean(scores)
```

Something that was very new to me in R was matrices. I learned how to create them and how to reference specific rows and columns.

```{r}
# Vector with numerics from 1 up to 10
my_vector <- 1:10 

# Matrix with numerics from 1 up to 9
my_matrix <- matrix(1:9, ncol = 3)

# First 10 elements of the built-in data frame mtcars
my_df <- mtcars[1:10,]

# Construct list with these different elements:
my_list <- list(my_vector,my_matrix,my_df)
```
